Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/approach.tex

\noindent\textbf{Deactivating Neurons On-The-Fly: }During the first stage,
ShrinkNets applies an on/off switch to every neuron of an initially over-sized
network. We model the on/off switches by multiplying each input (or output) of
each layer by a parameter $\bm{\theta}\in\{0,1\}$. A value of $0$
will deactivate the neuron, while $1$ will let the signal go through. These
switches are part of a new layer, called the \textbf{switch layer}; this layer applies 
to fully connected as well as convolutional layers.

Our objective is to minimize the number of ``on'' switches to reduce the model size as much
as possible while preserving prediction accuracy. This can be achieved by jointly
minimizing the objective of the network and a factor of the L0 norm of the
vector containing all the switches. Because finding an optimal binary
assignment is an NP-Hard problem, we relax the problem by allowing
 $\bm{\theta}$ to be a real number
instead of a binary value and constrain it using the L1 instead of L0 norm.

\noindent\textbf{Neuron Removal: } During this stage, the neurons that are
deactivated by the switch layers are actually removed from the network,
effectively shrinking the network size. This step improves inference
times, as we demonstrate in our evaluation. We choose to remove neurons at
training time because we have observed that this allows the remaining active neurons to adapt
to the new network architecture. Existing techniques focus on neuron removal
after training, and require an extra fine-tuning process to compensate for the
removal.\srm{cite something?}

@@

We want to tune the size of $L$ by applying a switch layer, $S$, containing $c$
switches.  The switch
layer is parametrized by a vector $\theta \in \mathbb{R}^c$ such that the result
of applying $S$ to $L(\bm{x})$ is a also a tensor size $\left(c \times d_1
\times \dots \times d_n\right)$ such that: 
%Suppose we wish to tune the size of $L$ by applying a switch layer.
%A switch layer $S$ applied to the output of $L$ can be parametrized by a 
%vector 
\begin{equation} 
S_{\theta}(L(\bm{x}))_{i,...} = \bm{\theta}_iL(\bm{x})_{i, ...} \forall i \in [1\ldots c]
\end{equation}
Once passed through the switch layer, each output channel $i$
produced by $L$ is scaled by the corresponding $\theta_i$. Note that when
$\theta_i = 0$, the $i^{\text{th}}$ channel is multiplied by zero and will not
contribute to any computation after the switch layer. If this happens, we say
the switch layer has {\it deactivated} the neuron corresponding to channel $i$ of layer $L$.

@@

%Formally, 
For training, we need to account for the effect of the switch layers on the loss
function. The effect of switch layers can be expressed in terms of a sparsity constraint
that pushes values in the $\theta$ vector to 0. In this way, given a neural network
parameterized by weights $\bm{W}$ and switch layer parameters $\bm{\theta}$, we
optimize ShrinkNet loss as follows 
\begin{equation}
\small
  L_{SN}(\bm{x},\bm{y};\bm{W}, \bm{\theta}) = L(\bm{x}, \bm{y}; \bm{W}) +
  \lambda\norm{\theta}_1 + \lambda_2\norm{\bm{W}}_p
\end{equation}
This expression augments the regular training loss with a regularization
term for the switch parameters and another on the network weights.

>>>>

\noindent\textbf{Deactivating Neurons On-The-Fly: }During the first stage,
ShrinkNets applies an on/off switch to every neuron of an initially over-sized
network. We model the on/off switches by multiplying each input (or output) of
each layer by a parameter $\bm{\beta}\in\{0,1\}$. A value of $0$
will deactivate the neuron, while $1$ will let the signal go through. These
switches are part of a new layer, called the \textbf{switch layer}; this layer applies 
to fully connected as well as convolutional layers.

Our objective is to minimize the number of ``on'' switches to reduce the model size as much
as possible while preserving prediction accuracy. This can be achieved by jointly
minimizing the objective of the network and a factor of the L0 norm of the
vector containing all the switches. Because finding an optimal binary
assignment is an NP-Hard problem, we relax the problem by allowing
 $\bm{\beta}$ to be a real number
instead of a binary value and constrain it using the L1 instead of L0 norm.

\noindent\textbf{Neuron Removal: } During this stage, the neurons that are
deactivated by the switch layers are actually removed from the network,
effectively shrinking the network size. This step improves inference times, as
we demonstrate in our evaluation. We choose to remove neurons at training time
because we have observed that this allows the remaining active neurons to adapt
to the new network architecture. Existing techniques focus on neuron removal
after training, and require an extra fine-tuning process to compensate for the
removal.\srm{cite something?} \gl{I think we are fine or we could actually
cite any of these paper}

@@

We want to tune the size of $L$ by applying a switch layer, $S$, containing $c$
switches.  The switch
layer is parametrized by a vector $\beta \in \mathbb{R}^c$ such that the result
of applying $S$ to $L(\bm{x})$ is a also a tensor size $\left(c \times d_1
\times \dots \times d_n\right)$ such that: 
%Suppose we wish to tune the size of $L$ by applying a switch layer.
%A switch layer $S$ applied to the output of $L$ can be parametrized by a 
%vector 
\begin{equation} 
S_{\beta}(L(\bm{x}))_{i,...} = \bm{\beta}_iL(\bm{x})_{i, ...} \forall i \in [1\ldots c]
\end{equation}
Once passed through the switch layer, each output channel $i$
produced by $L$ is scaled by the corresponding $\bm{\beta}_i$. Note that when
$\bm{\beta}_i = 0$, the $i^{\text{th}}$ channel is multiplied by zero and will not
contribute to any computation after the switch layer. If this happens, we say
the switch layer has {\it deactivated} the neuron corresponding to channel $i$ of layer $L$.

@@

%Formally, 
For training, we need to account for the effect of the switch layers on the loss
function. The effect of switch layers can be expressed in terms of a sparsity constraint
that pushes values in the $\bm{\beta}$ vector to 0. In this way, given a neural network
parameterized by weights $\bm{\theta}$ and switch layer parameters $\bm{\theta}$, we
optimize ShrinkNet loss as follows 
\begin{equation}
\small
  L_{SN}(\bm{x},\bm{y};\bm{\theta}, \bm{\beta}) = L(\bm{x}, \bm{y}; \bm{\beta}) +
  \lambda\norm{\beta}_1 + \lambda_2\norm{\bm{\theta}}_p^p
\end{equation}
This expression augments the regular training loss with a regularization
term for the switch parameters and another on the network weights.
